\chapter{Description of proposed chapter in thesis}
\label{ch:discription}

%2-3 pages
%A detailed description of what you should have in each
%chapter in your master thesis.

The master thesis will contain 4 chapters: Introduction, Methods, Results and Conclusion.
The introduction will start by broadly describing the thesis in simple terms, then explain the motivation behind the project,
the goal of the thesis, the current state of the art and finally the problem statement. 

The Methods chapter will describe the methods we have used in our research, why we used them and what makes
our research different from the current state of the art. It will describe the implementation of the human behavior,
the calculations regarding the evacuation speed and agress restricting factors as well as the implementation of the 
ship model. Furthermore, the methods chapter will contain the hypothesis.

The Results chapter will present the results and the evidence that either supports or oppose our hypothesis. The
statistical data gathered using the methods in the previous chapter will be displayed and any issues we will have had
will be explained.

The Discussion will look at what the data means, whether it matters or not and how it compares to other research in the field.
Additionally it will discuss how successful the project has been and if ACO is better than conventional algorithms, as we hypothesized.
Finally it will contain proposed future steps that can be made to continue developing the project.